---
title: "Hopper data"
author: "zdenek.vesely@gmail.com"
date: "1/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The map

```{r data}
library(tidyverse)
library(httr)

df <- readr::read_csv("puzzle.csv", col_names = c("x", "y"))

summary(df)

df %>% 
  head(32) %>% 
  knitr::kable()
```

There is `r nrow(df)` rows = 2^`r log(nrow(df), 2)`.

Lets Plot the data:

```{r plot0}
ggplot(df) +
  geom_point(aes(y, x)) +
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0)
```

It seems like the world.
As the x is in range `r range(df$x)` and y in `r range(df$y)`, it seems like the latitude and longitude in radian.

```{r positions}
positions_df <-
  df %>% 
  group_by(lat = x* 180 / pi, lon = y* 180 / pi) %>% 
  summarise(n_obs = length(x))

ggplot(positions_df) + 
  borders("world") +
  geom_point(aes(x = lon , y = lat, size = n_obs)) +
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) + 
  scale_size(trans="log10")
```

It maps to the map. But What are the points? Lets goggle it...

```{r prepare_google_maps_api}
GOOGLE_API_KEY <- readr::read_file("google_map_key.txt") # this is my private key, get yours to run it

positions_df <-
  positions_df %>% 
  mutate(api_call = 
           sprintf("https://maps.googleapis.com/maps/api/geocode/json?latlng=%s,%s&key=%s",
                   lat,
                   lon,
                   GOOGLE_API_KEY))

getLongAdress <- function(resp){
  adress_json <- content(resp,as="parsed")
  adress_json$results[[1]]$formatted_address
}

getTypes <- function(resp){
  adress_json <- content(resp,as="parsed")
  results <- adress_json$results
  n_res <- length(results)
  types <- character()
  for (i in 1:n_res){
    types <- c(types, unlist(adress_json$results[[i]]$types))
  }
  types %>% unique() %>% sort() 
}

```

```{r run_google_maps_api, eval = FALSE}
positions_with_adress_df <-
  positions_df %>% 
  mutate(resp = map(api_call, GET),
         long_adress = map(resp, getLongAdress)[[1]],
         types = map(resp, getTypes),
         isAirport = map(types, ~"airport" %in% .)[[1]]) %>% 
  select(-api_call, -resp) %>% 
  arrange(-n_obs) 
```

```{r load_pre_run, echo = FALSE}
load(file = "poz_with_adress.Rdata") 
positions_with_adress_df <- 
  poz_loc2 %>% 
  select(-api_call, -resp) %>% 
  arrange(-n_obs) 
```

```{r show_results}
positions_with_adress_df %>% 
  mutate(types = map(types, ~ paste(.,collapse = ", "))[[1]]) %>% 
  kableExtra::kable() %>%
  kableExtra::kable_styling() %>%
  kableExtra::scroll_box(height = "800px")
```

The `r positions_with_adress_df %>% ungroup() %>% summarise(mean(isAirport)) %>% pull() * 100`% of the records are recognized as airports.
(Manual check shows the others are also very near to airports.)


```{r save_it}
positions_with_adress_df %>% 
  select(-types) %>% 
  readr::write_csv("airports.csv")
```

But what is next? Why is there there exactly 2^10 records?
Why is there the Taiwan airport 101 times?


Are those just some random flight orders data from Hopper? 
Not likely, there would be much more repetition.